Paper figures

### 2019-05-21 voltagebudget/analysis/paper_figures_redraft.Rmd
WIP

# The trade off

```{r, fig.width=1.7, fig.height=2.8}
# Var
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc*mV, variances_pop*ms, group=freq)) +
  geom_point(size=.2, alpha=0.5) +
  xlab(expression(paste(V[o], " (mV)"))) +
  ylab("Variance (ms)") +
  theme_classic() -> p1
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc/V_comp, variances_pop*ms, group=freq)) +
  geom_point(size=.2, alpha=0.5) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  xlab(expression(V[o]/V[c])) +
  ylab("Variance (ms)") +
  theme_classic() -> p2

# Error
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc*mV, errors_pop*ms, group=freq)) +
  geom_point(size=.2, alpha=0.5) +
  xlab(expression(paste(V[o], " (mV)"))) +
  ylab("Error (ms)") +
  theme_classic() -> p3
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc/V_comp, errors_pop*ms, group=freq)) +
  geom_point(size=.2, alpha=0.5) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  xlab(expression(V[o]/V[c])) +
  ylab("Error (ms)") +
  theme_classic() -> p4

@@

tmp %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=variances_pop*ms, errors_pop*ms, group=freq, color=state)) +
  geom_point(size=.2, alpha=0.9) +
  xlab("Variance (ms)") +
  ylab("Error (ms)") +
  scale_color_manual("", values=c("darkslategray3", "darkslategray")) +
  theme_classic() -> p5

plot_grid <- rbind(
  c(NA, NA, NA, NA),
  c(1, 1, 3, 3), 
  c(1, 1, 3, 3),
  c(1, 1, 3, 3),
  c(1, 1, 3, 3),
  c(NA, NA, NA, NA),
  c(2, 2, 4, 4),
  c(2, 2, 4, 4),
  c(2, 2, 4, 4),
  c(2, 2, 4, 4),
  c(NA, NA, NA, NA),
  c(5, 5, 5, 5),
  c(5, 5, 5, 5),
  c(5, 5, 5, 5),
  c(5, 5, 5, 5),
  c(5, 5, 5, 5),
  c(5, 5, 5, 5))

By looking at the ratio we identified a narrow region (V_o/V_c ~< 0.27) where the trade-off is approx linear across freq, and that accounts for approx. half the total change in both variance and error. We hypothesize that this narrow region can be considered a healthy range for modulation as it is maximially sensitive (has the highest dirvative) and is approx. linear--representing the best possible trade-off irregardless of freq.

@@

# Vc and sync
```{r, fig.width=1.4, fig.height=1}
fig2 %>% 
  # filter(V_osc/V_comp <= ) %>%
  ggplot(aes(x=V_comp*mV, variances_pop*ms, color=V_osc*mV)) +
  geom_point(size=.2, alpha=0.5) +
  xlab(expression(paste(V[c], " (mV)"))) +
  ylab("Variance (ms)") +
  scale_color_gradient(expression(paste(V[o], " (mV)")), low="goldenrod1", high="firebrick3") +
  theme_classic() +
  theme(legend.key.width=unit(0.3,"cm"),
        legend.title=element_text(size=8),
        legend.text=element_text(size=8))
```

@@

# Freq. dependence
```{r, fig.width=0.65, fig.height=2.5}
fig2 %>% 
filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=variances_pop*ms, errors_pop*ms, group=freq)) +
  geom_point(size=.2, alpha=0.9) +
  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
  scale_y_continuous(breaks=c(0,30,60)) +
  xlab("Variance (ms)") +
  ylab("Error (ms)") +
  facet_grid(freq~.) +
  theme_classic() +
  theme(strip.text.y = element_text(angle=0), strip.background = element_blank())
```

```{r, fig.width=0.65, fig.height=2.5}
fig2 %>% 
  filter(V_osc/V_comp <= 0.8) %>%
  ggplot(aes(x=V_osc/V_comp, y=variances_pop*ms)) +
  geom_point(size=.2, alpha=0.5) +
  facet_grid(freq~.) +
  xlab(expression(V[o]/V[c])) +
  ylab("Variance (ms)") +
  scale_y_continuous(breaks=c(7.5,8,8.5,9)) +
  scale_x_continuous(breaks=c(0,0.4,0.8)) +
  # geom_rect(
  #   mapping=aes(xmin=0.15, xmax=0.4, ymin=min(variances_pop*ms), ymax=max(variances_pop*ms)),
  #   color="darkslategray4", fill="darkslategray4", alpha=0.02) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  theme_classic() +
  theme(strip.text.y = element_text(angle=0), strip.background = element_blank())
```

Fo far we've focused on error-variance relationships common between frequencies. Frequency also effect error-variance trade off.

...

Faster oscillations offer less sync overall, and therefore have a more limited var-error range than slower oscillations. If we use the curveture of the variance curve to fine tune the healthy ratio / frequency, we see that...

TODO: get max second deriv. Use that to find the change point?
TODO: plot max second derive ration point by freq. How does the healthy boundry scale with freq?

Slower oscillations have a wider working range, than faster oscillations. If doing stimulation experiments, once must also consider your freqeuncy carefully.

# Controls - Ws, noise, cell type
TODO

## Heterocells

```{r, fig.width=0.5, fig.height=1.4}
fig14 %>% 
  ggplot(aes(x=t, y=vm*1e3, group=cell)) +
  geom_line(size=0.2, color="black") +
  facet_grid(cell~.) +
  theme_classic() +
  labs(x="Time (s)", y="V (mV)") +
  theme(
    strip.text = element_blank(),
    strip.background = element_blank(),
    legend.position="none",
    axis.line=element_blank(),
    axis.text.x=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks=element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    panel.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p1
plot(p1)
```

```{r, fig.width=2.1, fig.height=1.5}
# --------------------------------------------------
# Cell type
fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 5) %>% 
  mutate(norm_errors = normalize(errors_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
  geom_point(size=.1, alpha=0.4) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  labs(x=expression(V[o]/V[c]), y="Norm. error", title="Cell type") +
  theme_classic() +
  theme(title = element_text(size=10)) +
  lims(x=c(0, 5)) -> p2

@@

```{r, fig.width=1.1, fig.height=2}
ms <- 1e3

>>>>

# The trade off
```{r, fig.width=2, fig.height=4}
# By freq
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc*mV, errors_pop*ms, group=freq, color=freq)) +
  geom_line(size=.5, alpha=0.8) +
  scale_colour_continuous("Freq.", low="lightsalmon1", high="orange4") +
  xlab(expression(paste(V[o], " (mV)"))) +
  ylab("Error (ms)") +
  theme_classic() +
  theme(legend.position="none") -> p1
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  ggplot(aes(x=V_osc*mV, variances_pop*ms, group=freq, color=freq)) +
  geom_line(size=.5, alpha=0.8) +
  scale_colour_continuous("Freq.", low="lightsalmon1", high="orange4") +
  xlab(expression(paste(V[o], " (mV)"))) +
  ylab("Variance (ms)") +
  theme_classic() +
  theme(
    legend.position=c(0.4, 1.5),
    legend.direction="horizontal",    
    legend.key.size = unit(.5, "cm"),
    legend.key.height=unit(0.3,"cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    legend.background = element_rect(colour ="black")) -> p2

# Norm
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=V_osc/V_comp, errors_pop, group=freq)) +
  geom_line(size=.5, alpha=0.5) +
  geom_hline(yintercept = 0.5, alpha=1, color="grey", linetype="dashed") +
  xlab(expression(V[o]/V[c])) +
  ylab("Norm. error") +
  theme_classic() -> p3
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=V_osc/V_comp, variances_pop, group=freq)) +
  geom_line(size=.5, alpha=0.5) +
  xlab(expression(V[o]/V[c])) +
  ylab("Norm. variance") +
  theme_classic() -> p4

# Budget
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=V_osc/V_comp, errors_pop, group=freq)) +
  geom_line(size=.5, alpha=0.5) +

  # Arrow
  # geom_segment(aes(x = 0.27, y = 0.5, xend = -.1, yend = 0.5), 
  #              color="darkslategray3", linetype="solid", size=.3,
  #              lineend = "round", linejoin = "round",
  #              arrow = arrow(length = unit(0.06, "npc"))) +
  # geom_segment(aes(x = .27, y = .5, xend = 0.27, yend = 0), 
  #              color="darkslategray3", linetype="solid", size=.3,
  #              lineend = "round", linejoin = "round",
  #              arrow = arrow(length = unit(0.06, "npc"))) +

  # X
  # geom_point((aes(x=0.27, y=0.5)), color="grey", size=3, shape=4, alpha=0.6) +

  # Line
  geom_vline(xintercept = 0.27, alpha=0.8, color="darkslategray3", linetype="solid") +
  xlab(expression(V[o]/V[c])) +
  ylab("Norm. error") +
  theme_classic() -> p5
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=V_osc/V_comp, variances_pop, group=freq)) +
  geom_line(size=.5, alpha=0.5) +

  # Arrow
  # geom_segment(aes(x = 0.28, y = 0.28, xend = -0.1, yend = 0.28), 
  #              color="darkslategray3", linetype="solid", size=.3,
  #              lineend = "round", linejoin = "round",
  #              arrow = arrow(length = unit(0.06, "npc"))) +
  # geom_segment(aes(x = .27, y = .28, xend = 0.27, yend = 0.0), 
  #              color="darkslategray3", linetype="solid", size=.3,
  #              lineend = "round", linejoin = "round",
  #              arrow = arrow(length = unit(0.06, "npc"))) +

  # Line
  geom_vline(xintercept = 0.27, alpha=0.8, color="darkslategray3", linetype="solid") +
  xlab(expression(V[o]/V[c])) +
  ylab("Norm. variance") +
  theme_classic() -> p6

@@

tmp %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>%
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
  geom_point(size=.8, alpha=0.8) +
  xlab("Norm. variance") +
  ylab("Norm. error") +
  scale_color_manual("", values=c("darkslategray3", "darkslategray")) +
  theme_classic() -> p7

plot_grid <- rbind(
  c(NA, NA, NA, NA),
  c(NA, NA, NA, NA),
  c(1, 1, 2, 2), 
  c(1, 1, 2, 2),
  c(1, 1, 2, 2),
  c(1, 1, 2, 2),
  c(NA, NA, NA, NA),
  c(3, 3, 4, 4),
  c(3, 3, 4, 4),
  c(3, 3, 4, 4),
  c(3, 3, 4, 4),
  c(NA, NA, NA, NA),
  c(5, 5, 6, 6),
  c(5, 5, 6, 6),
  c(5, 5, 6, 6),
  c(5, 5, 6, 6),
  c(NA, NA, NA, NA),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7),
  c(7, 7, 7, 7))

grid.arrange(p1, p2, p3, p4, p5, p6, p7, layout_matrix=plot_grid)
```

Error below 0.5 implies the result contains a majority of the reference. Beyond 0.5, the modulator dominates spiking. This means 0.5 serves as natural boundry to seperate oscillations that modulate other activity, and oscillations that activity. The ratio at 0.5 error is V_o/V_c = 0.27. This point turns out to several interesting features. It is where the trade-off is approx linear across freq, and where the trade-off is most stable.

We hypothesize that this narrow region of budget ratio can be considered a healthy range for modulation as it, let's comp dom, is maximially sensitive (has the highest dirvative) and is approx. linear is maximmally consistent--representing the best possible trade-off irregardless of freq.

@@

# Vc and sync
```{r, fig.width=1.4, fig.height=0.8}
fig2 %>% 
  filter(V_osc/V_comp <= 5) %>%
  group_by(freq, N) %>% 
  mutate(errors_pop = normalize(errors_pop)) %>%
  mutate(variances_pop = normalize(variances_pop)) %>%
  ggplot(aes(x=V_comp*mV, variances_pop, color=V_osc*mV)) +
  geom_point(size=.2, alpha=0.5) +
  xlab(expression(paste(V[c], " (mV)"))) +
  ylab("Norm. variance") +
  scale_color_gradient(expression(paste(V[o], " (mV)")), low="darkgrey", high="firebrick3") +
  theme_classic() +
  theme(legend.key.height=unit(0.3,"cm"),
        legend.key.width=unit(0.3,"cm"),
        legend.background = element_rect(colour ="black"),
        legend.title=element_text(size=8),
        legend.text=element_text(size=8))
```

@@

# Controls - Ws, noise, cell type
```{r, fig.width=2.1, fig.height=1.5}
# --------------------------------------------------
fig14 %>% 
  ggplot(aes(x=t, y=vm*1e3, group=cell)) +
  geom_line(size=0.2, color="black") +
  facet_grid(cell~.) +
  theme_classic() +
  labs(x="Time (s)", y="V (mV)") +
  theme(
    strip.text = element_blank(),
    strip.background = element_blank(),
    legend.position="none",
    axis.line=element_blank(),
    axis.text.x=element_blank(),
    axis.text.y=element_blank(),
    axis.ticks=element_blank(),
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    panel.background=element_blank(),
    panel.border=element_blank(),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p1

# Cell type
fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 5) %>% 
  mutate(norm_errors = normalize(errors_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
  geom_point(size=.1, alpha=0.4) +
  geom_vline(xintercept = 0.27, alpha=1, color="darkslategray3", linetype="solid") +
  labs(x=expression(V[o]/V[c]), y="Norm. error", title="Cell type") +
  theme_classic() +
  theme(title = element_text(size=10)) +
  lims(x=c(0, 5)) -> p2

@@

```{r, fig.width=1.1, fig.height=3}
ms <- 1e3
